|

### 2021-01-04 pre-analysis-plan/freire-skarbek-lynching.Rmd
add data and script

---
title:  |
        | Pre-Analysis Plan:
        | Casting the First Stone: Understanding Attitudes towards Lynching in Brazil[^thanks]
author:
  - Danilo Freire[^freire]
  - David Skarbek[^skarbek]
date: \today
abstract: "Why do citizens support extrajudicial violence? While endorsement for vigilantism has significantly decreased in advanced democracies, lynchings remain tolerated throughout the developing world. In this pre-analysis plan, we propose three survey experiments to investigate (i) which criminal profiles citizens prefer for extralegal punishment, (ii) how individuals justify mob violence, and (iii) whether information provision reduces support for vigilantism. First, we run a conjoint experiment to identify criminal characteristics that are associated with higher likelihood of lynching. In our second experiment, we show respondents a short article about a real lynching episode and ask them whether they see the mob's motivations as legitimate. Lastly, we test whether providing information about the legal consequences of lynching, human rights guarantees, and the risk of retribution makes respondents less likely to endorse extralegal violence. We will run the experiments in Brazil, a country which has seen a sharp rise in vigilante attacks and currently experiences one lynching attempt per day. Our survey will be conducted online and include 2,000 participants."
abstractspacing: double
keywords: Brazil, crime, extralegal violence, lynching, vigilantism
fontsize: 12pt
margin: 2cm
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    toc: no
    toc_depth: 3
    template: template.latex
---

>>>>

---
title:  |
        | Pre-Analysis Plan:
        | Casting the First Stone: Understanding Attitudes towards Lynching in Brazil[^thanks]
author:
  - Danilo Freire[^freire]
  - David Skarbek[^skarbek]
date: \today
abstract: "Why do citizens support extrajudicial violence? While endorsement for vigilantism has significantly decreased in advanced democracies, lynchings remain tolerated throughout the developing world. In this pre-analysis plan, we propose three survey experiments to investigate (i) which criminal profiles citizens prefer for extralegal punishment, (ii) how individuals justify mob violence, and (iii) whether information provision reduces support for vigilantism. First, we run a conjoint experiment to identify criminal characteristics that are associated with higher likelihood of lynching. In our second experiment, we show respondents a short article about a real lynching episode and ask them whether they see the mob's motivations as legitimate. Lastly, we test whether providing information about the legal consequences of lynching, human rights guarantees, and the risk of retribution makes respondents less likely to endorse extralegal violence. We will run the experiments in Brazil, a country which has seen a sharp rise in vigilante attacks and currently experiences one lynching attempt per day. Our survey will be conducted online and include 2,000 participants."
abstractspacing: double
keywords: Brazil, crime, extralegal violence, lynching, vigilantism
fontsize: 12pt
margin: 2cm
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: yes
    toc: no
    toc_depth: 3
    template: template.latex
---
